---
title: "ETC1010_Project_download"
author: "me"
date: "15/05/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


The code below downloads relevant libraries
```{r}
library(rtweet)
library(tidyverse)
library(tidytext)
```

The code below downloads a dataframe of tweets through the rtweet API

If you want to download tweets you need to get a twitter developer license which is free but takes a day or two to get approved. This code will not run because i have excluded my keys, check the bottom for a way to open the tweet tibble and look at it.
```{r}
appname <- "Learning through tweets"

## api key (example below is not a real key)
key <- "secret"

## api secret (example below is not a real key)
secret <- "secret"

access_token = "secret"

access_secret = "secret"

twitter_token <- create_token(
  app = appname,
  consumer_key = key,
  consumer_secret = secret,
  access_token = access_token,
  access_secret = access_secret)
```

This code downloads a dataframe of tweets. We have used it multiple times because it limits the volume of tweets that can be downloaded every 15 mins. max_id is set to specify the timing of the tweets.
```{r}
covid_tweets <- search_tweets(q = "covid -filter:retweets",
                               n = 15000,lang = "en",max_id = 1261704398777495561)

#we have set the language to english 
#n=15000 directs us to download 150000 tweets. 
```


I have saved the file as an RDS to preserve nested lists
```{r}
saveRDS(covid_tweets, file = "tweets_n.rds")
```

You can read an RDS like this:
```{r}
saved_data <- readRDS(file = "practice_tweets_set.rds")
saved_data
```

